Catching fire: Undefined behaviour for equational reasoning of lazy languages with strictness annotations

### 2021-01-19 paper/thesis.tex
add an actual thesis that is separate from the paper

@@

\subsection{Stretch: rewrite based unification}
\subsection{Stretch: rewrite based tabled typeclass generation}
\subsection{Stretch: As static as possible garbage collection}

>>>>

\section{Stuff that doesn't work}
\begin{itemize}
\item circular references: SSA by default cannot handle circular references.
      We need to use the "relaxed SSA" that allows graphs. It's unclear how well
      this adapts.
\item A garbage collector. The usual story here, we don't really make a fair
      comparison.
\item Any realistic program exhibiting "difficult" laziness. I feel what would
      be interesting would be to implement, say, GRIN, along with a sophisticated
      pointer analysis using the MLIR analysis-as-rewrite story here.
\item A proof of correctness of the naive demand analysis I wrote.
\end{itemize}

\section{Stuff that does work}
\begin{itemize}
\item An encoding of laziness that works for the simple stuff I've tried
\item A simple version of "demand analysis" that eliminates first order laziness.
\item Some toy examples where we generate better IR than GHC because we can
     expose the "real work" to LLVM/MLIR in a way that they understand, by
     eliminating the noise that is laziness.
\end{itemize}

\section{What I feel would make a good paper/thesis}
\begin{itemize}
\item Our story of performing worker/wrapper by outlining/inlining is
\emph{intriguing}. I don't think it's \emph{strong}. So, to remedy that, we can:
\item (1) Make our laziness encoding bulletproof, connect to CBPV for example,
          handle circular references, etc.
\item (2) Make a strong case that MLIR is an interesting target for this breed of language.
          So, perform unification in MLIR, typeclass resolution in MLIR, perform some
          analysis/optimisation. Ths way, we show an end-to-end prototype of something that
          sorta works, instead of one thing that sorta works (?)
\end{itemize}

@@

\subsection{Stretch: Separate dialect for pattern matching}
\subsection{Stretch: rewrite based demand analysis}
\subsection{Stretch: rewrite based unification}
We introduce a dialect for performing unification.

\subsection{Stretch: rewrite based tabled typeclass unification}
\subsection{Stretch: As static as possible garbage collection}
